Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
add plant ontology reference
add SPIN/OWL comparison reference

\subsection{Semantic validation}
PODD validates experiments using independently configurable rules based on OWL
(Web Ontology Language) schemas. Although PODD currently only supports OWL as a
rules language, it could be easily extended in other cases to use different
systems such as N3, RDFS, SPARQL, or SPIN as rules languages.

@@

An ontology is a common controlled vocabulary about a particular topic, in this
case plant phenomics. The PODD Plant ontology therefore becomes an ontology for
plant phenomics that extends the generally applicable PODD Science ontology with
plant phenomics specific details \cite{Li2010}. This approach allows PODD to model
multiple phenomics processes without enforcing a rigid data structure on
objects, either now, in the past, or in the future. In addition, other community
ontologies, such as the plant and gene ontologies [3, 4], can be used to
annotate the data. This not only supports data discovery, but provides common
reference points through which PODD managed data can be integrated with data in
other research databases.

@@

References
[1] http://www.iucr.org/\_\_data/iucr/lists/epc-l/pdf00003.pdf
[2] http://topbraid.org/spin/api/
[3] http://www.plantontology.org/
%[4] http://www.geneontology.org/
[5] https://wiki.csiro.au/confluence/display/dmsdoc/Home
[6] http://datatracker.ietf.org/doc/draft-kunze-bagit/
[7] https://pypi.python.org/pypi/bagit/
[8] http://sourceforge.net/projects/loc-xferutils/
[9] http://sourceforge.net/projects/loc-xferutils/files/loc-bagger/
%[10] https://wiki.csiro.au/display/ASC
%[11] doi:10.1109/COINFO.2009.66 
%[12] doi:10.1016/j.jbi.2008.03.004
%[13] doi:10.1007/978-3-642-13654-2\_22
%[14] http://www.w3.org/DesignIssues/LinkedData.html

>>>>

\subsection{Semantic validation}
PODD validates experiments using independently configurable rules based on OWL
(Web Ontology Language) schemas. Although PODD currently only supports OWL as a
rules language, it could be easily extended in other cases to use different
systems such as N3, RDFS, SPARQL, or SPIN as rules languages \cite{Fuerber2010}.

@@

An ontology is a common controlled vocabulary about a particular topic, in this
case plant phenomics. The PODD Plant ontology therefore becomes an ontology for
plant phenomics that extends the generally applicable PODD Science ontology with
plant phenomics specific details \cite{Li2010}. This approach allows PODD to model
multiple phenomics processes without enforcing a rigid data structure on
objects, either now, in the past, or in the future. In addition, other community
ontologies, such as the plant and gene ontologies \cite{Ashburner2000,Avraham2008}, can be used to
annotate the data. This not only supports data discovery, but provides common
reference points through which PODD managed data can be integrated with data in
other research databases.

@@

References
%[1] http://www.iucr.org/\_\_data/iucr/lists/epc-l/pdf00003.pdf
%[2] http://topbraid.org/spin/api/
%[3] http://www.plantontology.org/
%[4] http://www.geneontology.org/
[5] https://wiki.csiro.au/confluence/display/dmsdoc/Home
[6] http://datatracker.ietf.org/doc/draft-kunze-bagit/
[7] https://pypi.python.org/pypi/bagit/
[8] http://sourceforge.net/projects/loc-xferutils/
[9] http://sourceforge.net/projects/loc-xferutils/files/loc-bagger/
%[10] https://wiki.csiro.au/display/ASC
%[11] doi:10.1109/COINFO.2009.66 
%[12] doi:10.1016/j.jbi.2008.03.004
%[13] doi:10.1007/978-3-642-13654-2\_22
%[14] http://www.w3.org/DesignIssues/LinkedData.html
